---
title: "Davide Zambon (898103) - Exercise N 1"
output:
  html_document: 
    df_print: paged
    toc: true
    toc_float: true
    number_sections: true
---


# Point a solution
The constant k an be determined by guaranteeing the continuity of the function, by solving
$$
kx^2 = 1, \  \text{when} \ x=10
$$
the solution is 
```{r, error=TRUE}
k <- 1/100
k
```
# Point b solution
probability that job A is within specification: 
since we know k and we have the cdf, we can just compute: 
$$
F(B) -F(A)
$$
```{r, error=TRUE}
prob_A = k*8.37^2 - k*3.65^2
prob_A
```


# Point c solution
probability that job B is within specification:

point B is a uniform distribution, so the probability of lying between the interval is 
```{r, error=TRUE}
length_interest <- 8.37 - 3.65
length_total <- 12
prob_B <- length_interest / length_total
prob_B
```


# Point d solution
Compute the probability that a randomly selected job executed by the platform is within specification:

We can just compute the proportions:

```{r, error=TRUE}
prop_A <- 0.63
prop_B <- 1-prop_A

total_prob = prop_A * prob_A + prop_B * prob_B
total_prob
```

# Point e solution

we can use Bayes' Theorem
```{r, error=TRUE}
Pa_givenS = 0.63 * prob_A / total_prob
Pa_givenS
```



