---
title: "Davide Zambon (898102) - Exercise 2"
output:
  html_document: 
    df_print: paged
    toc: true
    toc_float: true
    number_sections: true
---


# Point a solution
The system can be described with a CTMC with 3 states:
State 1 (S) (Standby): The robot is waiting for a task.
State 2 (T) (Transporting): The robot is actively transporting items.
State 3 (C) (Charging/Maintenance): The robot is charging or undergoing maintenance.


# Point b solution
to write the generator, use the holding times and the given probability.
```{r, error=TRUE}
l_1 <- 1/11
l_2 <- 1/13
l_3 <- 1/10
```

from holding, it always move to transporting
```{r, error=TRUE}
q_st <- 1/11
q_sc <- 0
q_ss <- -1/11
```


from transporting
```{r, error=TRUE}
q_ts <- l_2 * 0.7
q_tc <- l_2 * 0.3
q_tt <- -(q_ts + q_tc)
```

from charging, always moves to Standby (S).
```{r, error=TRUE}
q_ct <- 0
q_cs <- 1/10
q_cc <- -1/10
```

finally,
```{r, error=TRUE}
library(MASS)
library(expm)
Q <- matrix(c(q_ss, q_sc, q_st,
              q_cs, q_cc, q_ct,
              q_ts, q_tc, q_tt), nrow = 3, byrow = TRUE)
Q
```

# Point c solution
to find the stationary, we an solve the system or either elevate the generator for a very high time

```{r, error=TRUE}
get_state_probability <- function(Q, pi0, t) {
  
  P_t <- expm(Q * t)
  pi_t <- pi0 %*% P_t
  
  return(list(
    "Transition_Matrix_Pt" = P_t,
    "Final_Distribution_pi_t" = pi_t
  ))
}
pi0 <- c(1, 0, 0)
time <- 20000
results <- get_state_probability(Q, pi0, time)
print("--- THE FINAL DISTRIBUTION pi(t) ---")
print(results$Final_Distribution_pi_t)
```

# Point d solution

using the same function as above,

```{r, error=TRUE}
pi0 <- c(1, 0, 0)
time <- 10
results <- get_state_probability(Q, pi0, time)
print(results$Final_Distribution_pi_t)

```



